Multi-level modeling with Openflexo/\FML

### 2022-02-25 9-relatedworks.tex
complete biblio.bib + fix redundant citation

A first description of process modeling as a multi-level modeling problem was
proposed by~\textcite{lara2018refactoring} in the context of a catalogue of
refactoring for multi-level models (in a simpler form with fewer constraints
and requirements w.r.t. the challenge version). A solution is provided with
MetaDepth~\parencite{metadepth}, which supports modeling with any number of
levels, dual ontological/linguistic typing and deep characterization through
potency~\parencite{potency}. For their solution to the multi-level process problem
they use three levels. The first level describes generic processes, the second
level software engineering processes, and the third level, software engineering
enacted processes. Additionally, the authors use~\emph{linguistic
extensions}~\parencite{metadepth}, a mechanism to  linguistically extend
ontological instance models at any level, in order to introduce artifact types
and tasks duration in the second level. Our solution is similar to theirs
w.r.t. the grouping and organization of concepts (\eg, a model for general process, concepts, an extension for software engineering process) but it replaces the use of clabjets and potency with the use of the type-object pattern~\parencite{typeObject}. The so-called \emph{linguistic extensions} are natively supported in Openflexo/\FML.

>>>>

A first description of process modeling as a multi-level modeling problem was
proposed by~\textcite{lara2018refactoring} in the context of a catalogue of
refactoring for multi-level models (in a simpler form with fewer constraints
and requirements w.r.t. the challenge version). A solution is provided with
MetaDepth~\parencite{metadepth}, which supports modeling with any number of
levels, dual ontological/linguistic typing and deep characterization through
potency~\parencite{atkinson2001essence}. For their solution to the multi-level process problem
they use three levels. The first level describes generic processes, the second
level software engineering processes, and the third level, software engineering
enacted processes. Additionally, the authors use~\emph{linguistic
extensions}~\parencite{metadepth}, a mechanism to  linguistically extend
ontological instance models at any level, in order to introduce artifact types
and tasks duration in the second level. Our solution is similar to theirs
w.r.t. the grouping and organization of concepts (\eg, a model for general process, concepts, an extension for software engineering process) but it replaces the use of clabjets and potency with the use of the type-object pattern~\parencite{typeObject}. The so-called \emph{linguistic extensions} are natively supported in Openflexo/\FML.
